---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mixIE

<!-- badges: start -->
<!-- badges: end -->

R package for Mendelian randomization with mixIE methods.

## Installation

<!-- You can install the released version of mixIE from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("mixIE")
```

-->

Install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("lin00374/mixIE")
```
## Example

Here is an example which shows how to apply mixIE methods to make inference about the causal effect from **Fast Glucose (FG)** to **Type-2 Diabetes (T2D)**

```{r example}
library(mixIE)
library(ggpubr)
head(FG_T2D)
```

Now we perform mixIE-MA with the outcome sample size 69033 and reorientating IVs with all positive associations with the exposure.

```{r mixIE-MA}
set.seed(1)
mixIE_MA_result = mixIE_MA(b_exp=FG_T2D$beta_hat_1,b_out=FG_T2D$beta_hat_2,
                           se_exp=FG_T2D$seb1,se_out = FG_T2D$seb2,
                           n=69033,flip=1)
mixIE_MA_result
```

We can also obtain the results for mixIE-MA when directly implementing mixIE-MA-DP:
```{r mixIE-MA-DP}
set.seed(1)
mixIE_MA_DP_result = mixIE_MA_DP(b_exp=FG_T2D$beta_hat_1,b_out=FG_T2D$beta_hat_2,
                           se_exp=FG_T2D$seb1,se_out = FG_T2D$seb2,
                           n=69033,flip=1)
mixIE_MA_DP_result
```

We can obtain the diagnostic plots of mixIE-MA-DP by setting `diagnostic_plot=TRUE`:
```{r diagnostic}
set.seed(1)
mixIE_MA_DP_result = mixIE_MA_DP(b_exp=FG_T2D$beta_hat_1,b_out=FG_T2D$beta_hat_2,
                           se_exp=FG_T2D$seb1,se_out = FG_T2D$seb2,
                           n=69033,flip=1,
                           diagnostic_plot = TRUE)
g1=ggarrange(mixIE_MA_DP_result$scatter_og.plot, mixIE_MA_DP_result$scatter_dp.plot,labels =c("A:mixIE-MA", "B:mixIE-MA-DP"),
            common.legend=TRUE,legend = 'bottom',font.label = list(size = 8))
g2=ggarrange(mixIE_MA_DP_result$iv_barplot, mixIE_MA_DP_result$est_hist,labels =c("C", "D"),
               legend = 'bottom',font.label = list(size = 8))
ggarrange(g1,g2,nrow = 2)
```


